An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets

### 2021-10-20 ju-hofmann/ju-hofmann.Rmd
correct a figure label

p1 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.max", 
                         subtitle = "npeaks.set: 5-3-1, seg_length: 50") +
  xlab(labels[3])
p2 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.maxbar",
                         subtitle = "npeaks.set: 5-3-1, seg_length: 50") +
  xlab(labels[4])
p.result1_252 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
               common.legend = TRUE, legend = "bottom")
p.result1_252 <- annotate_figure(p.result1_252, top = text_grob(com.title252))
p.result1_252
```

@@

```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks.set = c(5,3,1)} ", fig.height=3, warning=FALSE}
p1 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
                         subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
  xlab(labels[3])
p2 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
                         subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
  xlab(labels[4])
p.result1_44 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
               common.legend = TRUE, legend = "bottom")
p.result1_44 <- annotate_figure(p.result1_44, top = text_grob(com.title44))
p.result1_44
```

@@

>>>>

p1 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.max", 
                         subtitle = "npeaks.set: 5-3-1, seg_length: 50") +
  xlab(labels[1])
p2 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.maxbar",
                         subtitle = "npeaks.set: 5-3-1, seg_length: 50") +
  xlab(labels[4])

p.result1_252 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
               common.legend = TRUE, legend = "bottom")
p.result1_252 <- annotate_figure(p.result1_252, top = text_grob(com.title252))
p.result1_252
```

@@

```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks.set = c(5,3,1)} ", fig.height=3, warning=FALSE}
p1 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
                         subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
  xlab(labels[1])
p2 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
                         subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
  xlab(labels[4])
p.result1_44 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
               common.legend = TRUE, legend = "bottom")
p.result1_44 <- annotate_figure(p.result1_44, top = text_grob(com.title44))
p.result1_44
```

@@

<!-- ```{r plot_thisisus} -->
<!-- rf.252.plot <- metric_plot_helper(rf.results[[1]], "rf.diff", scaled = TRUE, -->
<!--                                   subtitle = "random forest scores with metric diff") + -->
<!--   xlab(expression(RF[diff])) + -->
<!--   scale_x_continuous(breaks = seq(0, 1, by = 0.1)) -->
<!-- cmps.252.plot <- metric_plot_helper(CMPS_hamby252_results_npeak$cmps.table[[8]], "cmps.diff_scaled",  -->
<!--                                     scaled = TRUE, subtitle = "CMPS, 10-8-6-4-2-1, 50") + -->
<!--   xlab(labels[3]) + -->
<!--   scale_x_continuous(breaks = seq(0, 1, by = 0.1)) -->

<!-- rf.44.plot <- metric_plot_helper(rf.results[[2]], "rf.diff", scaled = TRUE, -->
<!--                                   subtitle = "random forest scores with metric diff") + -->
<!--   xlab(expression(RF[diff])) + -->
<!--   scale_x_continuous(breaks = seq(0, 1, by = 0.1)) -->
<!-- cmps.44.plot <- metric_plot_helper(CMPS_hamby44_results_npeak$cmps.table[[6]], "cmps.diff_scaled",  -->
<!--                                     scaled = TRUE, subtitle = "CMPS, 10-7-4-2, 61") + -->
<!--   xlab(labels[3]) + -->
<!--   scale_x_continuous(breaks = seq(0, 1, by = 0.1)) -->

<!-- p.thisisus252 <- ggarrange(plotlist = list(cmps.252.plot, rf.252.plot), nrow = 1, ncol = 2, -->
<!--                common.legend = TRUE, legend = "bottom") -->
<!-- p.thisisus252 <-  -->
<!--   annotate_figure(p.thisisus252,  -->
<!--                   top = text_grob("Hamby 252 - Random Forest and CMPS")) -->

<!-- p.thisisus44 <- ggarrange(plotlist = list(cmps.44.plot, rf.44.plot), nrow = 1, ncol = 2, -->
<!--                common.legend = TRUE, legend = "bottom") -->
<!-- p.thisisus44 <-  -->
<!--   annotate_figure(p.thisisus44,  -->
<!--                   top = text_grob("Hamby 44 - Random Forest and CMPS")) -->

<!-- ``` -->
